---
title: "Super-Awesome Super-Resolution"
subtitle: "Applied Deep Learning"
author: "Weber Gerald, 0125536"
date: "1/23/2020"
output: 
  beamer_presentation:
      theme: "Rochester"
      colortheme: "seahorse"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Initiate

Improve existing super resolution generative adversarial network.

```{r, echo = FALSE, out.width="30%"}
myimages<-c('grumpy1.png', 'grumpy2.png', 'grumpy3.png')
knitr::include_graphics(myimages)
```

## Hacking

- Collect all the data.

- Succeeded CPU training.

- Failed CUDA.

- Failed improving.

- Failed transforming checkpoint model to tensorflow.js.

## Delivery

- Reused existing SR GAN.

- Implemented client/server app with Flask.

- Demo

## Take-aways

- Get an idea how GANs work.

- Can be hard to setup CUDA support (on Azure VM).

- PIP: need a new version to have access to Tensorflow2.

- Creating docker images is a tedious task.

- Use Flask for development environment only.

- Use early stopping.

## Thank you for your attention!

```{r, echo = FALSE}
myimages<-c('../report/screenshot.png')
knitr::include_graphics(myimages)

